---
author: "Your Name"
title: "Computer Project 2: Regression"
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Car Stopping Distance

The cars data set in R lists car speeds (in mph) and stopping distances (in ft).

```{r}
plot(cars$speed, cars$dist, xlab="Speed (mph)", ylab="Distance (ft)", col='blue')
```

The correlation between speed and distance is

```{r}
r = cor(cars$speed, cars$dist)
r
```

_Comment on the sign (+/-) and magnitude (close to 1 or close to 0) of the correlation._
\newpage


We can use regression to predict stopping distances for speeds not in the data set.

```{r}
model = lm(cars$dist ~ cars$speed)
plot(cars$speed, cars$dist, xlab="Speed (mph)", ylab="Distance (ft)", col='blue')
abline(model, col='green')
```

The following output gives information about the regression line.

```{r}
summary(model)
```

_Use the output to write down the equation for the regression line._

\newpage

The slope and y-intercept of the regression line are:
```{r}
b = model$coefficients[1]
b

m = model$coefficients[2]
m
```

The predicted stopping distance for a car going 20 mph is
```{r}
m * 20 + b
```

The RMS error for the regression line is

```{r}
rms = sd(cars$dist) * sqrt(1 - r**2)
rms
```

So, if a car is traveling at 20 mph, its stopping distance is `r m*20 + b` ft give or
take about `r rms` feet.

_Repeat the calculations above to predict the stopping distance of a car traveling 
at 25 mph._

_Comment on the accuracy of using the regression line to predict the stopping distance
of a car traveling at 75 mph._

\newpage

# Tree Volume 

The trees data set in R lists tree heights (ft), diamters (in) and volumes (cubic ft).

```{r}
plot(trees$Girth, trees$Volume, xlab="Girth (in)", ylab="Volume (cubic ft)", col='green')
```

```{r}
plot(trees$Height, trees$Volume, xlab="Height (ft)", ylab="Volume (cubic ft)", col='blue')
```

\newpage

_Based on the plots, which variable do you think would be better at predicting tree volume?_

The correlations of volume with the other variables are:
```{r}
cor(trees$Girth, trees$Volume)
cor(trees$Height, trees$Volume)
```

_Comment on the sign and magnitude of the two correlations._

_Fill in the blanks to find the regression line for predicting volume from one 
of the other variables.  Also remove the # symbols._

```{r}
#model = lm(trees$??? ~ trees$Volume)
#plot(trees$???, trees$Volume, xlab="???", ylab="Volume (cubic ft)"", col='blue')
#abline(model, col='green')
```

The following output gives information about the regression line.

```{r}
#summary(model)
```

_Use the output to write down the equation for the regression line._








